formula1: further tests

### 2020-03-12 inst/formula1_extra.Rmd
just the strongest 8

@@

Thus from the fourth row, for example, we see that in Russia the
conditions were dry and Vettel drove in pole position.  We might ask whether

```{r dotable}
TT <- table(wins=as.vector(f2017[1,1:20]==1),pole=cond$pole == "Hamilton")
fisher.test(TT)
```

We are going to use a generalization of function
\code{ordertable2supp()} that incorporates pole position and condition
information:

```{r,applydata}
```

@@

for(i in seq_len(nrow(fmat))){
  jj1 <- ordervec2supp(fmat[i,, drop=TRUE])
  pwa(jj1,as.vector(cond$pole[i]),"pole")
  out  <- out + pwa(jj1,as.vector(cond$pole[i]),"pole")
}
(mo <- maxp(out))
pie(mo)
```

Now we can use it to create a profile likelihood curve along the same
lines as table tennis

>>>>

Now we can consider only the strongest say 8 competitors.  There are
two ways to proceed.  Firstly, we can retain just the 8 strongest
competitors as estimated from the full likelihood function:

```{r,strongestnineanotherapproach,cache=TRUE}
mo8a <- sort(mo,decreasing=TRUE)[seq_len(8)]
pie(mo8a)
```

Or secondly, we can simply erase everyone but the first 8 from the
likelihood function `out`  and use that:

```{r,strongestnine,cache=TRUE}
out8 <- keep(out,seq_len(8))
head(out8)
mo8 <- maxp(out8)
dotchart(log(mo8))
pie(mo8)
```

Note how the two approaches are not equivalent: the second approach
has redistributed the estimated strengths and, for example, Ricciardo
has an estimated strength of essentially zero (because he consistently
loses to the other 7 players).

# Pole position

Driving pole position is an important thing:

@@

Thus from the fourth row, for example, we see that in Russia the
conditions were dry and Vettel drove in pole position.  We might ask
whether Hamilton's winning is associated with his driving at pole
position:

```{r makehamiltontable}
(TT <- table(wins=as.vector(f2017[1,1:20]==1),pole=cond$pole == "Hamilton"))
```

Thus from the above we see that, of Hamilton's 9 wins, 8 of them were
from pole; conversely, of his 11 pole races, he lost only 3.

```{r,fishertestpoleham}
fisher.test(TT)
```

We are going to use a generalization of function `ordertable2supp()`
that incorporates pole position and condition information:

@@

for(i in seq_len(nrow(fmat))){  # iterate through the races
  jj1 <- ordervec2supp(fmat[i,, drop=TRUE])      # jj1 is a LF for a single race...
  jj2 <- pwa(jj1,as.vector(cond$pole[i]),"pole") # jj2 includes a pole ghost racer
  out  <- out + jj2                              # now increment 'out' with ghost LF 
}
head(out)
```

In the above, we see ghost driver `pole`.

```{r,maximizeoutandpie,cache=TRUE}
(mo <- maxp(out))
pie(mo)
```

# Profile likelihood of pole strength

Now we can use it to create a profile likelihood curve along the same
lines as table tennis, but for simplicity we will keep just the
strongest 9 competitors:

```{r,justnine}
4+5
```
